A GRASP algorithm for the concrete delivery problem.

### 2023-05-26 Article/article.tex
correct model

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newcommand{\pcmaxc}{P$|\mbox{\em cont}|$C$_{\max}$\xspace}
\newcommand{\alns}{adaptive large neighborhood search\xspace}
\newcommand{\Alns}{Adaptive large neighborhood search\xspace}
\newcommand{\F}{$\mathcal{F}$\xspace}
\newcommand{\B}{$\mathcal{B}$\xspace}
\newcommand{\C}{$\mathcal{C}$\xspace}
\newcommand{\Lb}{$\mathcal{L}$\xspace}
\newcommand{\D}{$\mathcal{D}$\xspace}

@@

\section{Introduction}
\label{sec:intro}
Concrete is a widely used building material in construction projects. It is a perishable product that can be affected by many different factors that impact its quality \citep{sinha_quality_2021} which is crucial for the durability and strength of the final construction.

Concrete comes in two types: ready-mixed concrete (RMC) and site-mixed concrete (SMC). RMC is manufactured in a batch plant and delivered to the construction site, while SMC is produced on-site using raw materials stored on the construction site. Site-mixed concrete can avoid delays caused by road traffic, but it has a slower and more difficult production process, requires storage for mixing materials and equipment, and is suitable for low amounts of concrete. On the other hand, RMC has better quality and benefits from lower production costs \citep{muresan_comparing}. However, to take advantage of these benefits, the batch plant manager must ensure efficient and prompt delivery on the construction site, which may require a fleet of high-cost revolving drum trucks (concrete mixers) to dispatch the ready-mixed concrete.

Concrete delivery under the form of RMC is subject to many operational constraints that make it a challenging problem met in Operations Research and addressed by the Concrete Delivery Problem (CDP). In this paper, we study a variant of the Concrete Delivery Problem to schedule the daily production and dispatching of RMC for a company located in the province of Quebec, Canada. This company operates multiple batching plants with varying production rates, using a fleet of concrete mixers with different capacities. Each plant has its own fleet of trucks, however, the trucks are able to move between plants if necessary. The trucks must return to their home plant at the end of the day. The company owns two types of trucks with different capacities but also has the option to call on an external fleet when needed. They serve construction sites from any of their batch plants, with the first delivery starting at the time specified by the customer. The loading and unloading of a concrete mixer depend on the truck capacity, the loading rate at the plant, and the unloading rate at the construction site. Drivers are allocated based on their daily work schedules. A customer may request several types of concrete to be delivered within the same time window, with no required sequence for the orders, but an order can only start after the completion of the previous order. This constraint generalizes the linked order constraints of \cite{durbin2008or} where some customers place two orders for the same day and request that they are linked (the second order begins only after the first order is completed). The setting of this study is similar to a variant of the Concrete Delivery Problem previously studied in \cite{schmid2009hybrid, schmid2010hybridization}. However, it includes the plant's production rate and driver shift schedule and does not consider unloading instrumentation in contrast to the previous research.
The company uses a centralized dispatcher system to schedule all daily orders, but this system has issues satisfying all daily demands without using an external fleet.
% Also, as per union rules, they assign a truck driver to a delivery task based on his seniority.

According to \cite{blazewicz2019handbook}, the concrete delivery problem combines vehicle routing with scheduling issues to plan routes to deliver concrete from batch plants (depots) to customers' construction sites. Ready-mixed concrete is an on-demand product with a short life cycle from production through end use. It cannot be stored and cannot stay too long in a truck, or it will harden. Hence, concrete mixers must deliver RMC at the planned construction site shortly after its production. RMC production and delivery is described by \cite{tommelein1999just} as an example of a Just-In-Time (JIT) production system in construction. A customer quantity requirement is often greater than the truck size and must be fulfilled by multiple deliveries. In that sense, CDP is like the Vehicle Routing Problem (VRP) with split delivery (VRPSD) \citep{archetti2008split}, except that the same truck may visit a customer more than once. Concrete hardens quickly, so when there are multiple deliveries, they must be done back-to-back or at least close in time to avoid the problem of cold joint, which can reduce the strength and durability of the concrete. Customers request to be served within a specific time window, which can complicate truck-loading schedules when a plant can only load one truck at a time. Similarly, only one truck can unload at a time at a customer location, sometimes leading to concrete mixers queuing and waiting their turn to deliver. Furthermore, with trucks of varied sizes, loading, travel, and unloading times that may be uncertain, the Concrete Delivery Problem is a complex problem to solve and has been proven to be NP-hard \citep{asbach2009analysis,kinable2014concrete}.

In this paper, we propose a mathematical model and a Greedy Randomized Search Procedure (GRASP) heuristic solution to solve a new variant for the CDP. Our model takes into consideration the working shifts of the drivers and the scheduling of multiple orders within the same time window at a construction site. To the best of our knowledge, this paper is the first that deals with these specific constraints in the context of the CDP.

The rest of the paper is structured as follows: Section \ref{lit_review} provides a literature review of previous work related to the CDP. Section \ref{desc_form} provides a formal description and mathematical model of the problem. In Section \ref{method}, we describe the Greedy Randomized Search Procedure algorithm and the constructive heuristics developed to solve this variant of the CDP. Section \ref{comp_exp}  presents computational experiments to evaluate the proposed approach, and finally, the conclusions are presented in Section \ref{concl}.

@@

A text mining approach by \cite{maghrebi2015text} for reviewing the ready-mixed concrete literature showed that concrete technology and material science are the main core of research in this area. Academic research on concrete batching and delivery began in the late 1990s. \cite{tommelein1999just} described ready-mixed concrete (RMC) as a prototypical example of a Just-In-Time production system in construction and identified two practices for delivering it. One approach is for the customer to haul the product from the batch plant with their concrete mixer, while the other approach is for the batch plant to deliver the concrete directly to the customer's location. This latter approach is the one that has been studied in all related papers found in the literature.

Several works to schedule and dispatch concrete production and delivery have mainly focused on simulation-related methods. These methods can be standalone, such as those used by \cite{zayed2001simulation, wang2001scheduling, tian_simulation_based_2010, panas_simulation_based_2013} and \cite{galic2016simulation}, among others. Alternatively, these methods can be hybridized with optimization techniques, such as those used by \cite{feng2004optimizing, lu2005optimized, feng_integrating_2006}, etc. \cite{wang2001scheduling} developed a simulation model to reveal the effect and value of the concrete mixers' inter-arrival time on the productivity of hired unloading equipment on site. \cite{feng2004optimizing} used a combination of Genetic Algorithm (GA) and simulation process to minimize the total waiting time for trucks at a customer site. The study focused on loading trucks with identical capacities at the same batch plant, with fixed loading and unloading durations. The GA was used to find the best loading sequence of RMC trucks to be assigned to different construction sites. The simulation process determined the loading, arrival, departure, and waiting time of trucks and thus evaluated the cost of each dispatching sequence. They evaluated their method using data from a batch plant in Taiwan with up to nine customers served. \cite{mayteekrieangkrai2015optimized} addressed the same problem with the same data using a bee algorithm (BA) and found better solutions than the GA. \cite{lu2005optimized} used the same combination of GA and simulation to determine the optimal number of concrete mixers to be deployed and an optimal schedule for batching and delivering concrete. Their objective was to minimize the idle time of the site crew due to late concrete deliveries and truck queuing time. In this setting, it was also necessary to deliver a batch of mortar on-site to lubricate the unloading pump before the concrete delivery. As such, the simulation model also included the batching and delivery of mortar. Finding the best RMC truck size was also the purpose of the discrete-event simulation model proposed by \cite{panas_simulation_based_2013}.

In addition to simulation-based methods, several other approaches have been used in the literature to solve the CDP. These include metaheuristics \citep{faria2006distributed, misir2011selection, maghrebi2016sequential, yang2022concrete}, exact methods \citep{yan2007optimal, asbach2009analysis, kinable2014concrete}, matheuristics \citep{schmid2009hybrid, schmid2010hybridization}, Benders Decomposition \citep{maghrebi2014benders}, Column Generation (CG) \citep{maghrebi2014solving, maghrebi2016column}, Lagrangian relaxation \citep{narayanan2015using}, and machine learning approaches such as those used by \cite{graham2006modeling, maghrebi2014exploring, maghrebi2016matching}. \cite{matsatsinis2004towards} designed a decision support system (DSS) for the dynamic routing of both concrete and pumps that may be necessary for some construction sites to aid in the unloading of concrete. The DSS considered the availability of three plants but stipulated that vehicles fulfilling the same order must all load at the same plant. Orders that could not be executed immediately could be postponed for the next day. The routing of the pumps was modelled as a multi-depot vehicle routing problem with time windows. \cite{naso2007genetic} proposed a sequential GA method combined with constructive heuristics to solve another variant of the CDP. In this problem, the plant's production schedule must account for orders for concrete to be delivered to a customer site and orders that customers must pick up themselves. The algorithm first schedules the plant loading operations before scheduling truck deliveries. The authors also developed a non-linear model that minimizes transportation costs, waiting times, outsourced costs, and overtime work. They ran experiments using real-world instances of a concrete supply chain in the Netherlands and found a reduction in the number of requests redirected to external companies. \cite{yan2007optimal} also considered overtime considerations in their paper, which focused on scheduling RMC for one batching plant with two loading docks. The study took into account that overtime wages are paid for factory and construction site operations after 4 PM. They developed a mixed integer programming (MIP) model on a time-space network to minimize travel times and operating costs at both normal and overtime working hours at the plant and the construction sites. They tested the model using real-data consisting of 3 days of operation using a two-stage algorithm. First, they solved the MIP relaxation with CPLEX. Then, they simplified the original model by fixing some decision variables before solving it. The algorithm was found to improve the actual plant operation by 10\%. A time-space network is the key component of the real-time decision support system (DSS) developed by \cite{durbin2008or} to solve a dynamic CDP problem every five minutes. The DSS is able to receive new orders, schedule them on the fly, and handle unexpected events such as plant closures, truck breakdowns, and delays in transportation times. The authors combined the DSS with a Tabu Search (TS) heuristic to warm start CPLEX, which made the model performant enough to solve instances with up to 1,500 loads per day with up to 250 trucks. The DSS also considers the case of a customer who places two orders, with the first being completed before the second starts. Further insights on the real-time planning and monitoring of CDP are available in \cite{garza2021dynamic}. Another variant of the CDP is modeled by \cite{schmid2009hybrid} as an integer multicommodity network flow (MCNF) problem on a time-space network. In this paper, concrete is delivered using a heterogeneous fleet of vehicles, and each plant can load an unlimited number of trucks simultaneously. Some of the trucks have specialized equipment and must arrive first at certain construction sites to assist in unloading the concrete. The objective is to fulfill all orders, minimize the travel cost, and avoid delays between two consecutive unloading operations for an order. The model is typically solved using a matheuristic algorithm that combines the MCNF with a variable neighborhood search (VNS) heuristic. The method can quickly solve large problem instances with more than 60 orders per day without encountering any memory issues. The same problem is addressed by \cite{schmid2010hybridization} who proposed a mixed integer programming (MIP) model combined with a VNS and a very large neighborhood search (VLNS) to develop two matheuristics approaches. Comparisons between both matheuristics and a standalone VNS show that the former methods are much better and suitable for solving larger problem instances. These methods also provide better solutions for small to medium instances than the matheuristic used in \cite{schmid2009hybrid}. A pure VNS approach with the same problem but without the use of instrumentation has been applied by \cite{payr2009optimizing}.

Regarding objectives, most authors have focused on minimizing travel time and delays between consecutive deliveries. However, some authors have been more interested in maximizing customer satisfaction alone. We find these situations in the works of \cite{durbin2008or, kinable2014concrete, kinable2014logic, sulaman2017simulated}. \cite{kinable2014concrete} introduce a general MIP and constraint programming (CP) models of the CDP reflecting the main constraints commonly found in all CDP works: time lag and no overlapping between consecutive deliveries, covering of all customers' demands, delivery time window, and heterogeneous fleet. However, the model did not include constraints limiting the time that concrete may reside in a truck. The authors propose a constructive heuristic that schedules the visits to the customers one by one according to the start time of the visit and the truck capacity. The procedure is invoked multiple times for different permutations of the customer's order which is determined using the steepest descent (SD) local search procedure. One of the paper's main contributions is the creation of the first public test instances for the CDP with up to 50 customers, four batching plants, and 20 concrete mixers. They found the CP model to be highly effective in finding high-quality solutions in relatively little time or improving existing schedules, while the MIP model can be used to compute bounds, as it seems ineffective in solving large problem instances. Finally, the heuristic often yields good solutions in less than a second. A detailed analysis of the MIP model presented in cite{kinable2014concrete}and of two more compact models can be found in the thesis of \cite{hernandez_lopez_study_2020}. In \cite{kinable2014logic}, we found an attempt to solve the previous problem with a Logic Based Benders' approach. \cite{sulaman2017simulated} expand upon the SD heuristic proposed in \cite{kinable2014concrete}, proposing a Simulated Annealing (SA) with a Time-Slot Heuristic (TH). TH mechanism is to look for a slot between existing visits of a truck to schedule a new delivery instead of assigning it to the time slot strictly after the truck's latest assigned delivery. The goal is to reduce the large time gaps that can be present in a schedule created with SD due to ignoring the intermediate available time slots. Experimental results indicated that SATH outperforms SD in speed and solution quality. A generalization of the MIP model of \cite{kinable2014concrete} is addressed in \cite{asbach2009analysis}. This model simultaneously minimizes the total sum of travel costs and the penalty costs for customers with unfulfilled demand. A customer can request that all concrete deliveries come from the same plant or a subset of plants and that a delivery truck belongs to a subset of the vehicle fleet. The MIP model is used in a local search scheme as a black-box solver to reoptimize an incumbent solution in which a neighborhood operator has unfixed some variables. \cite{tzanetos2023systematic} provides an overview of the various methods used in the literature to address the Concrete Delivery Problem and categorizes the problem formulations based on the different concepts used in the literature, such as Integer Programming (IP), time-space network, and job shop model. They also discussed the consistency between industry needs and existing constraints and provided insights into the datasets corresponding to real-world cases, identifying the necessary data for practitioners.

\section{Problem description}
\label{desc_form}
The focus of this paper is the distribution of ready-mixed concrete from a Canadian company that operates in the greater Montreal area. When a customer places an order, it is received at a central center and then assigned to one of the company's batching plants. These plants produce the concrete and then deliver it to the customer. The problem we are examining involves a set of batching plants, a set of customer orders, and a set of concrete-mixer drivers.

@@

The company owns a total of eight batching plants, located in various geographical regions. Each plant has a loading bay that can only accommodate one truck at a time, which leads to trucks lining up. Let $\mathcal{B}$ be the set of batching plants. The plants are heterogeneous, as each plant has its own hourly loading rate, represented by $\tau^l_b$, which affects the duration of the loading process. After the concrete has been loaded, the driver spends $\alpha_b$ minutes adjusting the concrete in the truck before heading to the customer site. A batching plant can serve a construction site as long as the travel time between the two is less than the concrete's lifespan, which is represented by $\Delta$. Each plant has its own assigned fleet of trucks, but it can also borrow trucks from other plants or hire external fleets if necessary.

A customer $i$ requests a total of $q_i$ of one or several types of concrete to be delivered to his construction site on a particular day.  We call an order a request for a specific type of concrete. When placing an order $o$, the customer $i$ specifies the required quantity, $q_o$, the desired arrival time of the first concrete mixer, $a_i$, and the unloading rate at their construction site, $\tau^u_i$. If the order requires more concrete than a single truck can carry, multiple deliveries are scheduled. Let $O_i$ be the unordered set of all orders requested by customer $i$. Each element of $O_i$ must be thoroughly delivered before moving on to another order. One element $o$ of $O_i$ must have its first delivery start at $a_i$, while the others can start any time after all deliveries of $o$. Once a plant is chosen to produce a customer's first delivery, it must be the provider of all subsequent deliveries of this customer. To prevent cold joint issues with the concrete, subsequent deliveries must be made just in time, or at least close in time. We define a maximum time lag $\gamma_i$ beyond which no next unloading operation should be allowed. The construction site unloading rate and the quantity to unload give the time necessary to discharge a truckload. $\mathcal{C}$ is the set of construction sites (customers) with a planned delivery for the day. $\mathcal{O}$ is the set of all requested orders.

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newcommand{\pcmaxc}{P$|\mbox{\em cont}|$C$_{\max}$\xspace}

\newcommand{\GRASP}{Greedy randomized adaptive search procedure\xspace}
\newcommand{\F}{$\mathcal{F}$\xspace}
\newcommand{\B}{$\mathcal{B}$\xspace}
\newcommand{\C}{$\mathcal{C}$\xspace}
\newcommand{\LB}{$\mathcal{L}$\xspace}
\newcommand{\Lb}{$\mathcal{L}_b$\xspace}
\newcommand{\D}{$\mathcal{D}$\xspace}
 \newcommand*{\red}{\textcolor{red}}

@@

\section{Introduction}
\label{sec:intro}
Concrete is a widely used building material in construction projects. Its perishable nature is affected by many factors that impact its quality \citep{sinha_quality_2021}, which is crucial for the durability and strength of the final construction. Concrete comes in two types: ready-mixed concrete (RMC) and site-mixed concrete (SMC). RMC is manufactured in a batch plant and delivered to the construction site, while SMC is produced on-site using raw materials stored on the construction site. Using SMC can avoid delays caused by road traffic, but it has a slower and more difficult production process, requires storage for mixing materials and equipment, and is suitable for low amounts of concrete. On the other hand, RMC has better quality and benefits from lower production costs \citep{muresan_comparing}. However, to take advantage of these benefits, the batch plant manager must ensure efficient and prompt delivery on the construction site, which may require a fleet of high-cost revolving drum trucks (concrete mixers) to dispatch the RMC.

Concrete delivery under the form of RMC is subject to many operational constraints that make the Concrete Delivery Problem (CDP) very challenging. In this paper, we study a variant of the CDP to schedule the daily production and dispatching of RMC for a company located in the province of Quebec, Canada. This company operates multiple batching plants with varying production rates, using a fleet of concrete mixers of different capacities. Each plant has its own fleet of trucks; however, under certain conditions, the trucks can move between plants if necessary. The trucks must return to their home plant at the end of the day. The company owns two types of trucks with different capacities and can call on an external fleet when needed. They serve construction sites from any of their plants, with the first delivery starting at the time specified by the customer. The loading and unloading of a concrete mixer depend on the truck capacity, the loading rate at the plant, and the unloading rate at the construction site. Drivers are allocated based on their daily work schedules. A customer may request several types of concrete to be delivered within the same time window, with no required sequence for the orders, but an order can only start after the completion of the previous order. This constraint generalizes the linked order constraints of \cite{durbin2008or} where some customers place two orders for the same day and request that they are linked (the second order begins only after the first order is completed). The setting of our study is similar to a variant of the CDP previously studied in \cite{schmid2009hybrid, schmid2010hybridization}. However, we include the plant's production rate and driver shift schedule. The company uses a centralized dispatcher system to schedule all daily orders, but this system has issues satisfying all daily demands without using an external fleet.
% Also, as per union rules, they assign a truck driver to a delivery task based on his seniority.

According to \cite{blazewicz2019handbook}, the CDP combines vehicle routing with scheduling issues to plan routes to deliver concrete from batch plants (depots) to customers' construction sites. RMC is an on-demand product with a short life cycle from production through end use. It cannot be stored and cannot stay too long on a truck, or it will harden. Hence, concrete mixers must deliver RMC at the planned construction site shortly after its production. \cite{tommelein1999just} describes RMC production and delivery as an example of a just-in-time (JIT) production system in construction. A customer quantity requirement is often greater than the truck size and must be fulfilled by multiple deliveries. In that sense, CDP is similar to the vehicle routing problem with split delivery \citep{archetti2008split}, except that the same truck may visit a customer more than once. Concrete hardens quickly, so multiple deliveries must be done back-to-back or at least close in time to avoid the problem of cold joint, which can reduce the strength and durability of the concrete. Customers request to be served within a specific time window, which can complicate truck-loading schedules when a plant can only load one truck at a time. Similarly, only one truck can unload at a time at a customer location, sometimes leading to concrete mixers queuing and waiting their turn to deliver. Furthermore, with trucks of varied sizes, loading, travel, and unloading times that may be uncertain, the CDP is a complex and challenging problem.

In this paper, we propose a mathematical model and a Greedy Randomized Search Procedure (GRASP) heuristic solution to solve a new variant of the CDP. Our model takes into consideration the working shifts of the drivers and the scheduling of multiple orders within the same time window at a construction site. To the best of our knowledge, this paper is the first that deals with these specific constraints in the context of the CDP.

The rest of the paper is structured as follows: Section \ref{lit_review} provides a literature review of previous work related to the CDP. Section \ref{desc_form} provides a formal description and mathematical model of the problem. In Section \ref{grasp_method}, we describe the GRASP algorithm and the constructive heuristics developed to solve this variant of the CDP. Section \ref{comp_exp}  presents computational experiments to evaluate the proposed approach, and finally, the conclusions are presented in Section \ref{concl}.

@@

Academic Research on concrete batching and delivery began in the late 1990s. \cite{tommelein1999just} described RMC as a prototypical example of a JIT production system in construction and identified two practices for delivering it. One approach is for the customer to haul the product from the batch plant with their concrete mixer, while the other is for the batch plant to deliver the concrete directly to the customer's location. This latter approach is the one that has been studied in all related papers found in the literature. Several works to schedule and dispatch concrete production and delivery have mainly focused on simulation-related methods. These methods can be standalone, such as those used by \cite{zayed2001simulation, wang2001scheduling, tian_simulation_based_2010, panas_simulation_based_2013} and \cite{galic2016simulation}, among others. Alternatively, these methods can be hybridized with optimization techniques, such as those used by \cite{feng2004optimizing, lu2005optimized}, and \cite{feng_integrating_2006}. \cite{wang2001scheduling} developed a simulation model to reveal the effect and value of the concrete mixers' inter-arrival time on the productivity of hired unloading equipment on site. \cite{feng2004optimizing} used a combination of genetic algorithm (GA) and simulation process to minimize the total waiting time for trucks at a customer site. The study focused on loading trucks with identical capacities at the same batch plant, with fixed loading and unloading durations. The GA was used to find the best loading sequence of RMC trucks to be assigned to different construction sites. The simulation process determined the loading, arrival, departure, and waiting time of trucks and thus evaluated the cost of each dispatching sequence. They evaluated their method using data from a batch plant in Taiwan with up to nine customers served. \cite{mayteekrieangkrai2015optimized} addressed the same problem with the same data using a bee algorithm (BA) and found better solutions than the GA. \cite{lu2005optimized} used the same combination of GA and simulation to determine the optimal number of concrete mixers to be deployed and an optimal schedule for batching and delivering concrete. Their objective was to minimize the idle time of the site crew due to late concrete deliveries and truck queuing time. In this setting, it was also necessary to deliver a batch of mortar on-site to lubricate the unloading pump before the concrete delivery. As such, the simulation model also included the batching and delivery of mortar. Finding the best RMC fleet size was also the purpose of the discrete-event simulation model proposed by \cite{panas_simulation_based_2013}.

In addition to simulation-based methods, several other approaches have been used in the literature to solve the CDP. These include metaheuristics \citep{faria2006distributed, misir2011selection, maghrebi2016sequential, yang2022concrete}, exact methods \citep{yan2007optimal, asbach2009analysis, kinable2014concrete}, matheuristics \citep{schmid2009hybrid, schmid2010hybridization}, Benders Decomposition \citep{maghrebi2014benders}, column generation (CG) \citep{maghrebi2014solving, maghrebi2016column}, Lagrangian relaxation \citep{narayanan2015using}, and machine learning approaches such as those used by \cite{graham2006modeling, maghrebi2014exploring, maghrebi2016matching}. \cite{matsatsinis2004towards} designed a decision support system (DSS) for the dynamic routing of both concrete and pumps that may be necessary for some construction sites to aid in the unloading of concrete. The DSS considered the availability of three plants but stipulated that vehicles fulfilling the same order must all load at the same plant. Orders that could not be executed immediately could be postponed for the next day. The routing of the pumps was modeled as a multi-depot vehicle routing problem with time windows. \cite{naso2007genetic} proposed a sequential GA method combined with constructive heuristics to solve another variant of the CDP. In this problem, the plant's production schedule must account for orders for concrete to be delivered to a customer site and orders that customers must pick up themselves. The algorithm first schedules the plant loading operations before scheduling truck deliveries. The authors also developed a non-linear model that minimizes transportation costs, waiting times, outsourced costs, and overtime work. They ran experiments using real-world instances of a concrete supply chain in the Netherlands and found a reduction in the number of outsourced requests. \cite{yan2007optimal} also considered overtime considerations in their paper, which focused on scheduling RMC for one batching plant with two loading docks. The study took into account that overtime wages are paid for factory and construction site operations after 4 PM. They developed a mixed-integer programming (MIP) model on a time-space network to minimize travel times and operating costs at both normal and overtime working hours at the plant and the construction sites. They tested the model using real data consisting of three days of operation using a two-stage algorithm. First, they solved the MIP relaxation with CPLEX. Then, they simplified the original model by fixing some decision variables before solving it. The algorithm was found to improve the actual plant operation by 10\%. A time-space network is the key component of the real-time DSS developed by \cite{durbin2008or} to solve a dynamic CDP every five minutes. The DSS is able to receive new orders, schedule them on the fly, and handle unexpected events such as plant closures, truck breakdowns, and delays in transportation times. The authors combined the DSS with a tabu search (TS) heuristic to warm start CPLEX, which made the model performant enough to solve instances with up to 1,500 loads per day with up to 250 trucks. The DSS also considers the case of a customer who places two orders, with the first being completed before the second starts. Further insights on the real-time planning and monitoring of CDP are available in \cite{garza2021dynamic}. Another variant of the CDP is modeled by \cite{schmid2009hybrid} as an integer multicommodity network flow (MCNF) problem on a time-space network. In this paper, concrete is delivered using a heterogeneous fleet of vehicles, and each plant can load an unlimited number of trucks simultaneously. Some of the trucks have specialized equipment and must arrive first at certain construction sites to assist in unloading the concrete. The objective is to fulfill all orders, minimize the travel cost, and avoid delays between two consecutive unloading operations for an order. The model is typically solved using a matheuristic algorithm that combines the MCNF with a variable neighborhood search (VNS) heuristic. The method can quickly solve large problem instances with more than 60 orders per day without encountering any memory issues. The same problem is addressed by \cite{schmid2010hybridization}, who proposed a MIP model combined with a VNS and a very large neighborhood search (VLNS) to develop two matheuristics approaches. Comparisons between both matheuristics and a standalone VNS show that the former methods are much better and suitable for solving larger problem instances. These methods also provide better solutions for small to medium instances than the matheuristic used in \cite{schmid2009hybrid}. A pure VNS approach with the same problem but without the use of instrumentation has been applied by \cite{payr2009optimizing}.

Regarding objectives, most authors have focused on minimizing travel time and delays between consecutive deliveries. However, some authors have been more interested in maximizing customer satisfaction alone. We find these situations in the works of \cite{durbin2008or, kinable2014concrete, kinable2014logic, sulaman2017simulated}. \cite{kinable2014concrete} introduce a general MIP and constraint programming (CP) models of the CDP reflecting the main constraints commonly found in all CDP works: time lag and no overlapping between consecutive deliveries, covering of all customers' demands, delivery time window, and heterogeneous fleet. However, the model did not include constraints limiting the time that concrete may reside in a truck. The authors propose a constructive heuristic that schedules the visits to the customers one by one according to the start time of the visit and the truck capacity. The procedure is invoked multiple times for different permutations of the customer's order which is determined using the steepest descent (SD) local search procedure. One of the paper's main contributions is the creation of the first public test instances for the CDP with up to 50 customers, four batching plants, and 20 concrete mixers. They found the CP model to be highly effective in finding high-quality solutions in a relatively short time or improving existing schedules, while the MIP model can be used to compute bounds, as it seems ineffective in solving large problem instances. Finally, the heuristic often yields good solutions in less than a second. A detailed analysis of the MIP model presented in \cite{kinable2014concrete} and of two more compact models can be found in the thesis of \cite{hernandez_lopez_study_2020}. In \cite{kinable2014logic}, we found an attempt to solve the previous problem with a logic-based Benders' approach. \cite{sulaman2017simulated} expand upon the SD heuristic proposed in \cite{kinable2014concrete}, proposing a simulated annealing (SA) combined with a time-slot Heuristic (SATH). This method looks for a slot between existing visits of a truck to schedule a new delivery instead of assigning it to the time slot strictly after the truck's latest assigned delivery. The goal is to reduce the large time gaps that can be present in a schedule created with SD due to ignoring the intermediate available time slots. Experimental results indicated that SATH outperforms SD in speed and solution quality. A generalization of the MIP model of \cite{kinable2014concrete} is addressed in \cite{asbach2009analysis}. This model simultaneously minimizes the total sum of travel costs and the penalty costs for customers with unfulfilled demand. A customer can request that all concrete deliveries come from the same plant or a subset of plants and that a delivery truck belongs to a subset of the vehicle fleet. The MIP model is used in a local search scheme as a black-box solver to reoptimize an incumbent solution in which a neighborhood operator has unfixed some variables. \cite{tzanetos2023systematic} provide an overview of the various methods used in the literature to address the CDP and categorizes the problem formulations based on the different concepts used in the literature. They also discussed the consistency between industry needs and existing constraints and provided insights into the datasets corresponding to real-world cases, identifying the necessary data for practitioners.

\section{Problem description}
\label{desc_form}
The focus of this paper is on the distribution of RMC from a Canadian company that operates in the greater Montreal area. When a customer places an order, it is received at a control center and assigned to one of the company's batching plants. These plants produce the concrete and then deliver it to the customer. The problem we are examining involves a set of customer orders, a set of concrete-mixer drivers, and a set of batching plants.

A customer $i$ requests one or more types of concrete to be delivered to their  construction site on a particular day, starting at time $a_i$.  We call an order $o$ a request for a specific type of concrete.  $q_i$ is the sum of the demands $q_o$ of each order $o$ placed, $a_i$ is the desired arrival time of the first concrete mixer, and $\tau^u_i$ is the unloading rate for customer $i$. If the order requires more concrete than a single truck can carry, multiple deliveries are scheduled.

Let $O_i$ be the set of all orders requested by customer $i$. Each element of $O_i$ must be fully delivered before moving on to another order. Exactly one order $o$ of $O_i$ must have its first delivery start at $a_i$, while the others can start at any time after $o$ is completed. Once a plant is selected to produce a customer's first delivery, it must be the supplier of all subsequent deliveries from that customer. To avoid cold joint problems with the concrete, the subsequent deliveries must be made in close succession. We define a maximum time delay $\gamma_i$ after which no more deliveries are allowed. The customer unloading rate and the quantity to be unloaded give the time required to unload a truckload. Let $\mathcal{C}$ be the set of construction sites (customers) with a planned delivery for the day, and $\mathcal{O}=\{{O_i, i \in \mathcal{C}}\}$ be the set of all requested orders for all customers.

The company has two types of concrete mixer trucks with capacities of 8 and 12 cubic meters. Each driver $k$ is assigned to a particular batch plant and is responsible for driving a truck with capacity $Q_k$. The set of drivers is represented by $K =\cup_{b \in \mathcal{B}}K_b $, where $K_b$ is the set of drivers scheduled to start their shift at batch plant $b$. $t_{ij}$ is the known time to travel between any two locations $i$ and $j$.
A scheduled driver $k$ is required to start his shift at $H_k$, work a minimum of $M_T$ hours and a maximum of $N_T$ hours during regular working hours, with the possibility of overtime of up to $O_T$ hours. $\beta_3$ and $\beta_4$ are the penalties incurred if a driver works less than $M_t$ and more than $N_t$.

A driver typically loads RMC at his assigned batch plant but may be required to drive to and load at other plants if needed. The batch plant produces concrete on demand using recipes specific to each order. This means that a truck can only haul RMC for one order, even if there is spare capacity.  After unloading the RMC,  driver $k$ takes $Ct_k$ minutes to clean the concrete mixer before proceeding. %When assigning drivers to deliveries, the company prioritizes employees with the highest seniority.

Let $n_o$ be the number of deliveries needed to fulfill the order $o$. $n_o$ is not known in advance because we use a fleet of trucks with different capacities. However, we can compute its lower ($n_o^{min}$) and upper ($n_o^{max}$) bounds using the capacities of the largest ($Q_{max}$) and smallest ($Q_{min}$) available trucks. 
\begin{alignat}{3}
    \label{mod:c0}
       n_o^{min} = \left\lceil \frac{q_o}{Q_{max}} \right\rceil \leq n_o \leq n_o^{max} = \left\lceil \frac{q_o}{Q_{min}} \right\rceil  & \text{ } & 
 \forall  o \in \mathcal{O}.
\end{alignat}

Let $d^j_{o}$ be the $j^{th}$ visit with load $q^j_{o}$ for order $o$. We represent the fulfillment of order $o$ by the visits to the ordered set of delivery nodes $\mathcal{D}_o= \left(d^0_{o},d^1_{o},\cdots, d^{n_o}_{o}\right)$. The deliveries of customer $i$ are the ordered set $\mathcal{D}_i= (\mathcal{D}_{o_1}, \mathcal{D}_{o_2},\cdots,\mathcal{D}_{o_{|O_i|}})$, where $o_r$ is the $r^{th}$ delivered order. We will refer to $d \in \mathcal{D}_i$ ($d \in \mathcal{D}_o$) as the $d^{th}$ potential delivery of customer $i$ (order $o$). $\mathcal{D}=\bigcup_{i\in \mathcal{C}} \mathcal{D}_i$ is the union of all delivery nodes.

@@

The company owns a total of eight batching plants. Each plant has a loading dock that can accommodate only one truck at a time, which leads to trucks lining up. Let $\mathcal{B}$ be the set of batching plants. The plants are heterogeneous, as each plant $b$ has its own hourly loading rate, represented by $\tau^l_b$, which affects the duration of the loading process. After loading the concrete, the driver spends $\alpha_b$ minutes adjusting the concrete in the truck before heading to the customer site. Each plant has its own assigned fleet of trucks, but it can borrow trucks from other plants. % or hire external vehicles if necessary. 
 A batching plant can serve a construction site as long as the travel time between the two is less than the concrete's lifespan, which is represented by $\Delta$. Let $l_{bj}$ be the loading dock node associated with delivery node $j$ at plant $b$.
We represent each plant $b$ by the set $\mathcal{L}_b = \{l_{bj}, t_{bj}\leq  \Delta, j \in \mathcal{D} \}$  of loading docks nodes. $\mathcal{L}=\bigcup_{b\in B} \mathcal{L}_b$ is the union of all loading docks.

% \subsection*{Model}
A solution to the problem involves decisions about truck loading schedules, driver assignments to different deliveries, and truck arrival times at construction sites for unloading. For a batching plant, the decision involves choosing which driver to \textcolor{red}{load}, when to load them, and which construction site they should deliver to. For a driver, the decision involves determining the sequence of loading depots and delivery sites. And for a construction site, the decision involves determining the arrival times of all scheduled deliveries for the day.

Each driver leaves and returns to their home plant every day. We represent the home plant of a driver $k$ with a starting depot $s_k$ and an ending depot $e_k$. $S$ and $E$ are the sets of starting and ending depots, respectively.
